Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-06-11 Masterarbeit_Robotik_Pamuk.tex
cpuaffinity.sh

\section{Host OS Configurations}\label{sec:host_configurations}
\subsection{CPU isolation}\label{subsec:cpu_isolation}

@@

>>>>

\section{Host OS Configurations}\label{sec:host_configurations}
\subsection{CPU affinity and isolation}\label{subsec:cpu_isolation}

@@

Additionally, the CPU affinity of IRQ threads of NVME (Non-Volatile Memory Express, a type of SSD storage) can be set away from CPU 4 to avoid impacting real-time workloads running on CPU 4. This can be done through finding out the respective process IDs through \texttt{ps -e | grep 'irq/.*nvme'} and then executing \texttt{sudo taskset -a -p -c 0 <PID>} with the PID obtained from the previous command.
